---
title: "A Simple weather app using shiny"
author: "Sayef Ishauqe"
date: "November 28, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

A simple weather app that shows weather info on a map

- Takes a city as input
- Zoom to the city on the map
- Shows Weather details in a pop-up

## Technical components

- Shiny
- Leaflet
- Esri worldTopoMap
- owmr - for fetching weather info from openWeatherMap

owmr requries an API key to fetch weather information. For further info visit [openWeatherMap website](https://openweathermap.org/current])

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(owmr)
library(leaflet)
api_key<-"fdb99d731200dcf32a5f2b48463456f1"
```

## Fetching weather info
```{r cars, echo = TRUE}
#library(owmr)
#api_key<-"xxxxxxxxxxxxxxxxxxxxxxxxxxxxxx"

city<-"Toronto"
owmr::owmr_settings(api_key = api_key)
res <- get_current(city, units = "metric") %>%
            flatten()

popcontent <- paste(sep = "<br/>", 
                           paste("City:",res$name),
                           paste("Desc:",res$weather.main),
                           paste("Temp:",res$main.temp))

popcontent
```

## Plotting result on map

```{r map, echo=TRUE, fig.height=5, message=FALSE, warning=FALSE}

leaflet() %>%
               addProviderTiles("Esri.WorldTopoMap") %>%
               setView(lng=res$coord.lon,lat=res$coord.lat, zoom = 5) %>%
               addPopups(lng=res$coord.lon,lat=res$coord.lat,
                                     popup = popcontent)

```

